### 2021-03-01 crowd-forecast/email-templates/email-template.Rmd
update email template

@@

### Quota issues

One last thing. As you may have experienced, we sometimes experience issues when too many people try to log in at the same time. We are using Google drive to store and load the forecasts and are getting an error that says "Quoata exceeded". Usually, this shouldn't happen at our usage level. We made a Stackoverflow question about it [here](https://stackoverflow.com/questions/66186332/googlesheets-quota-limit-issues-possible-failure-to-use-api-key). In case you have thoughts on that or know people who might, please reach out!

@@

>>>>

### The European Forecast Hub

On March 8th, the [European Forecast Hub](https://covid19forecasthub.eu/) will launch. Our crowd forecast app will therefore be expanded to include a set of 32 countries. If you like you can stick to forecasting Germany and Poland, but more observations will be available. We'll send more detailed information around next week.

### Introduction video

To help new forecasters get used to the user interface, we created a [short video](https://www.youtube.com/watch?v=NzZkNxXFgm8) that explains how to make a forecast. If you like, check it out.

@@

@@

PPS: We solved our quota issues. Thank you very much for your helpful comments last week!
